Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-02-10 aosd13/pepm13/caseStudyDiscussion.tex
Discussion of optimizations

>>>>

\section{Optimization limitations}
\label{sec:optim-vs-inc}
\pg{Resume}
While indexing achieved significant speedups, when indexing does not apply
speedups are more limited; in comparison, later projects working on collection
query optimization gave better speedups.

A design goal of this project was to incrementalize optimized queries, and while
it is easy to incrementalize collection operators such as \texttt{map},
\texttt{flatMap} or \texttt{filter}, it was much less clear to us how to
optimize the result of inlining.
We considered using shortcut fusion, but we did
not know a good way to incrementalize the resulting programs; later work, as
described in \cref{part:incr}, clarified what is possible and what not.

Another problem is that most fusion techniques are designed for sequential processing, hence conflict with incrementalization.
Most fusion techniques generally assume bulk operations scan collections in
linear order. For instance, shortcut fusion rewrites operators in terms of
\texttt{foldr}. It is not so clear how to extend them to parallel and
incremental programs. \pg{Cite Guy Steele talk against cons, and Ingo Maier's
  incremental library.}
